Barneby Lives usage example

### 2023-05-12 scripts/project_template.Rmd
included string parsing to describe site

out1 <- political_grabber(dummy_pts, 'collectionNo')
out2 <- place_grabber(dummy_pts)
out3 <- physical_grabber(dummy_pts)

out <- out1 %>% 
  dplyr::mutate(
    Gen = paste0(
      Country, ', ', State, ', ', County, ' Co., ', Mang_Name, " ", Unit_Nm, " ", trs), 
    Gen = stringr::str_replace_all(Gen, "NA", ""), 
    Gen = stringr::str_replace_all(Gen, "  ", ""))

>>>>

out1 <- political_grabber(dummy_pts, 'collectionNo')
out2 <- place_grabber(dummy_pts)
out3 <- physical_grabber(dummy_pts)
```
